Think again?\\ The amount of mental simulation tracks uncertainty in the outcome

### 2015-04-28 manuscript.tex
Put correlations in a table

\usepackage{amsmath, amsthm, amssymb}
\usepackage{graphicx}
\usepackage{color}

@@

% space below "Figure 1: ...", but only for inline figures
%\addtolength{\textfloatsep}{-0.1cm}

@@

We computed Pearson correlations between the model and people with 95\% confidence intervals computed from 10000 bootstrap samples. The fitted model explains participants' judgments of whether the ball would go in the hole very well (\HoleResponseCorr{}, see Figure \ref{fig:model-results}A), and can additionally account for how quickly participants responded to trials (\HoleRTCorr{}, see Figure \ref{fig:model-results}B).
Even if the number of bounces is not included, the \textsc{sprt} model with \threshold{} is able to account for a moderate amount of the variance in response times (\NoBouncesHoleRTCorr{}).

A model that takes only one sample each time (equivalent to \textsc{sprt} with $T=1$) does slightly better at explaining people's responses (\RawHoleResponseCorr{}) and about as well at explaining RT (\NoSamplesHoleRTCorr{}) as the full model.
However, this model cannot explain the variation of RT within bounces, while the full model can.
For the model with $T=1$, the correlation of RT for zero bounces was \NoSamplesHoleRTCorrZeroBounces{}; for one bounce, it was \NoSamplesHoleRTCorrOneBounce{}; and for two bounces, it was \NoSamplesHoleRTCorrTwoBounces{}.
In contrast, for the model with $T=2$, the correlation of RT for zero bounces was \HoleRTCorrZeroBounces{}; for one bounce, it was \HoleRTCorrOneBounce{}; and for two bounces, it was \HoleRTCorrTwoBounces{}.
The model with $T=1$ also fares slightly worse overall according to both BIC and AIC (for $T=1$, \BicNoSamples{} and \AicNoSamples{}; for $T=2$, \BicFull{} and \AicFull{}).

@@

>>>>

\usepackage{amsmath, amsthm, amssymb}
\usepackage{graphicx}
\usepackage{color}
\usepackage{booktabs}

@@

% space below "Figure 1: ...", but only for inline figures
\addtolength{\textfloatsep}{0.1cm}

@@

We computed Pearson correlations between the model and people with 95\% confidence intervals computed from 10000 bootstrap samples. The fitted model explains participants' judgments of whether the ball would go in the hole very well (\HoleResponseCorr{}, see Figure \ref{fig:model-results}A).
A model that takes only one sample each time (equivalent to \textsc{sprt} with $T=1$) does slightly better at explaining people's responses (\RawHoleResponseCorr{}).
As shown in Table \ref{tbl:rt}, both models do equally well at explaining overall RT in terms of correlation.
According to both BIC and AIC, the $T=1$ model does slightly worse (\BicNoSamples{} and \AicNoSamples{}) than the full model (\BicFull{} and \AicFull{}).
Moreover, the $T=1$ model cannot explain variance in RTs within bounces, whereas the full model with $T=2$ can (Table \ref{tbl:rt}).
If the number of bounces is excluded entirely, the full model can predict human RTs to a moderate degree (\NoBouncesHoleRTCorr{}), while the model with $T=1$ cannot predict RTs at all.

@@

\begin{table}
    \begin{tabular}{ccl}
    \toprule
    \textbf{Threshold} & \textbf{Bounces} & \textbf{Correlation} \\
    \midrule
    $T=1$ & 0   & \NoSamplesHoleRTCorrZeroBounces{} \\
          & 1   & \NoSamplesHoleRTCorrOneBounce{} \\
          & 2   & \NoSamplesHoleRTCorrTwoBounces{} \\
          & all & \NoSamplesHoleRTCorr{} \\
    \midrule
    $T=2$ & 0   & \HoleRTCorrZeroBounces{} \\
          & 1   & \HoleRTCorrOneBounce{} \\
          & 2   & \HoleRTCorrTwoBounces{} \\
          & all & \HoleRTCorr{} \\
    \bottomrule
    \end{tabular}
    \caption{Correlations between human and model RTs.}
    \label{tbl:rt}
\end{table}
